Approximation as Differentiation

### 2025-05-06 appendix/notes/auto-diff-galois-slicing-via-fam.tex
That's it for now, might switch to the view where we think of the objects in Fam(X,C) (X-indexed families of objects) as functors from X-as-discrete-category to C.

@@

Recall that $\Fam(\LatGal)$ is the Grothendieck construction $\Grothendieck{X}\Fam(X, \LatGal)$ which has:
\begin{itemize}
\item as objects $(X, \partial X)$ all pairs of a set $X$ and and for each $x \in X$, a bounded lattice
$\partial X_x$;
\item as morphisms $(X, \partial X) \to (Y, \partial Y)$, all pairs $(f, \partial f)$ of functions $f: X \to
Y$ and Galois connections $\partial f: \partial X_x \to \partial Y_{f(x)}$.
\end{itemize}

The action of $\Fam(-,\LatGal)$ on a morphism $f: X \to Y$. Composition of any $(f, \partial f):$

@@

Recall that $\Fam(\FinVect)$ denotes the Grothendieck construction $\Grothendieck{X}\Fam(X, \FinVect)$.
Consider the functor $\Diff \hookrightarrow \Fam(\FinVect)$ which send objects $\RR^n$ to constant families of
tangent spaces $(\RR^n, \const(\RR^n))$ and morphisms $f: \RR^m \to \RR^n \times (\RR^m \linearto \RR^n)$ to
pairs $(f_1, f_2)$ of differentiable functions $f_1: \RR^m \to \RR^n$ and families of linear maps $f_2:
\{{f_2}_x: \RR^m \linearto \RR^n\}_{x \in \RR^m}$. This exhibits $\Diff$ as equivalent to a full subcategory
of $\Fam(\FinVect)$.

>>>>

Recall that $\Fam(\cat{C})$ is the Grothendieck construction $\Grothendieck{X}\Fam(X, \cat{C})$.

@@

$\Fam(\LatGal)$ has:
\begin{itemize}
\item as objects $(X, \partial X)$ all pairs of a set $X$ and and for each $x \in X$, a bounded lattice
$\partial X_x$;
\item as morphisms $(X, \partial X) \to (Y, \partial Y)$, all pairs $(f, \partial f)$ of functions $f: X \to
Y$ and Galois connections $\partial f: \partial X_x \to \partial Y_{f(x)}$.
\end{itemize}

\todo{This is the basic setting for interpreting first-order programs.}

@@

Consider the functor $\Diff \hookrightarrow \Fam(\FinVect)$ which send objects $\RR^n$ to constant families of
tangent spaces $(\RR^n, \const(\RR^n))$ and morphisms $f: \RR^m \to \RR^n \times (\RR^m \linearto \RR^n)$ to
pairs $(f_1, f_2)$ of differentiable functions $f_1: \RR^m \to \RR^n$ and families of linear maps $f_2:
\{{f_2}_x: \RR^m \linearto \RR^n\}_{x \in \RR^m}$. This exhibits $\Diff$ as equivalent to a full subcategory
of $\Fam(\FinVect)$.
